Computing in the Field of Rationals

### 2012-06-22 rational_ext.tex
changes to the test code and first few sections of the paper

Compact Closed Structure (modulo 0).

@@

The following coherence conditions hold (see 2.1 in
\cite{selinger2007dagger}):

\begin{enumerate}
\item {{uniti (;) (eta* (;) swap(*)id) (;)(swap* (*) id) (;) assocr* (;) (id (*) eps*) (;) swap* (;) unite = id}}
\end{enumerate}

@@

>>>>

@@

\noindent
such that the following coherence conditions hold (see 2.1 in
\cite{selinger2007dagger}):

\begin{enumerate}
\item {{uniti (;) swap* (;) (id (*) eta*) (;) assocl* (;) ((swap* (;) eps*) (*) id) (;) unite = id : b <-> b}}
\item {{uniti (;) (eta* (*) id) (;) assocr* (;) (id (*) (swap* (;) eps*)) (;) swap* (;) unite = id : 1/b <-> 1/b}}

%% z_shape1Times :: a :<=> a
%% z_shape1Times = UnitI
%%                 :.: CommuteTimes
%%                 :.: (Id :*: EtaTimes) 
%%                 :.: AssocTimesL
%%                 :.: ((CommuteTimes :.: EpsTimes) :*: Id)
%%                 :.: UnitE

%% z_shape2Times :: Inv a :<=> Inv a
%% z_shape2Times = UnitI
%%                 :.: (EtaTimes :*: Id)
%%                 :.: AssocTimesR
%%                 :.: (Id :*: (CommuteTimes :.: EpsTimes))
%%                 :.: CommuteTimes
%%                 :.: UnitE

@@

TODO: once the semantics are written, write out the proof of one of
the coherence conditions in full.
